% !TEX program = lualatex

\documentclass[11pt]{article}
\usepackage{parskip} % To skip indentations %
\usepackage{enumitem} % Reduce space in itemize %
\pagenumbering{gobble} % Remove page numbers %
\usepackage[draft=false]{hyperref} % Add hyperlinks %

% Colors %
\usepackage{xcolor}
\definecolor{black}{HTML}{626162}
\definecolor{blacker}{HTML}{000000}
\definecolor{blue}{HTML}{4185F5}
\definecolor{darkblue}{HTML}{3164B7}
\definecolor{red}{HTML}{E14434}
\definecolor{green}{HTML}{0D9D5C}
\definecolor{yellow}{HTML}{F3B403}

% Font % 
\usepackage{fontspec}
\setmainfont[ExternalLocation=fonts/roboto/]{regular.ttf}[
    BoldFont=bold.ttf,
    ItalicFont=italic.ttf,
    BoldItalicFont=bolditalic.ttf]
%\setmainfont{Arial}

% Paper Size % 
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=0.5in}

% Commands %
\let\origsection\section
\renewcommand{\section}[2]{
    \origsection*{\LARGE \color{#2}#1} \hrule
}

\renewcommand{\subsection}[4]{
    \textcolor{#4}{\large \textbf{#1} \textit{-- #2} \hfill {#3}}
}

\begin{document}
% Header %
{\large
    {\Huge Tommy Josepovic} \hfill  \textbf{\href{http://www.github.com/tommy-josepovic}{github.com/tommy-josepovic}}\\
    tommy.josepovic@gmail.com\hfill Typescript, Python, Java, .NET,\\
    +1 (438) 497-4978 \hfill Angular, React, GraphQL, Flask
    % \hspace*{0pt} to make \hfill work on new lines
}

% Education %
\section{Education}{blacker}
\subsection{Concordia University}{B. Software Engineering}{September 2018 -- Present}{blacker}
\begin{itemize}[noitemsep]
    \item 3.82 / 4.30 GPA
    \item Dean's List
    \item Co-op student
    \item Graduation in May 2022
    
\end{itemize}
\subsection{Jean-de-Brébeuf College}{D.E.C. Sciences, Letters and Arts}{September 2016 -- May 2018}{blacker}

% Experience %
\section{Experience}{blacker}
\subsection{Desjardins Group}{Programmer}{May 2020 -- Present}{blacker}
\begin{itemize}[noitemsep]
    \item Reduced deployment time from 10 minutes to 5 minutes by rebuilding our pipelines.
    \item Migrated our repository from TFS to Azure DevOps.
    \item Built a C\# application to automatically migrate our backlog from TFS to Jira Server.
    \item Modernized the front-end of our .NET application by migrating to new technologies.
\end{itemize}
\subsection{Diff Agency}{Web Developer}{August 2019 -- December 2019}{blacker}
\begin{itemize}[noitemsep]
    \item Developed many pages and features for the Shopify websites of different clients.
    \item Ensured websites were compliant to modern web accessibility standards.
    \item Efficiently worked in different teams and on many projects.
\end{itemize}

% Projects %
\section{Projects}{blacker}
\subsection{EmotionLive}{Angular, Typescript, Firebase}{}{blacker}
\begin{itemize}[noitemsep]
    \item Collaborated on an application meant to help children with disabilities recognize and learn emotions by playing small web games. 
    \item Won the popularity prize against 120 other teams during Concordia's 2020 ConUHacks.
\end{itemize}

\subsection{ror2-editor}{React, Typescript}{}{blacker}
\begin{itemize}[noitemsep]
    \item Built a web app to allow people to modify their savefiles for the video game Risk of Rain 2.
\end{itemize}

%\subsection{Shoppies}{React, GraphQL, Apollo, Typescript}{blacker}
%\begin{itemize}
%    \item Built Shoppies, a movie browser web app built on top of the OMDB API. 
%\end{itemize}

%\subsection{tommy-josepovic.github.io}{Gatsby, GraphQL, Typescript}{}{blacker}
%\begin{itemize}[noitemsep]
%    \item Built a modern JAMStack personal site with Gatsby.
%\end{itemize}

\subsection{ShutterFeed}{Angular, Typescript, Firebase}{}{blacker}
\begin{itemize}[noitemsep]
    \item Developed  an image sharing social platform.
    \item 3 month group project made following Agile development practices.
\end{itemize}

% Activity & Rewards %
\section{Activity \& Rewards}{blacker}
Junior Achievement Quebec VP TI Award, Golden Key Society Invitation, Musical Theatre Actor, Volleyball.

\end{document}
